---
title: "Project2"
author: "Li Wu"
date: "2025-03-06"
output: pdf_document
---


```{r library}
library(dplyr)
library(tidyr)  # Load the package
library(tibble)
library(ChainLadder)
```


```{r}
A <- matrix(c(
  357848, 1124788, 1735330, 2218270, 2745596, 3319994, 3466336, 3606286, 3833515, 3901463,
  352118, 1236139, 2170033, 3353322, 3799067, 4120063, 4647867, 4914039, 5339085, NA,
   290507, 1292306, 2218525, 3235179, 3985995, 4132918, 4628910, 4909315, NA, NA,
  310608, 1418858, 2195047, 3757447, 4029929, 4381982, 4588268, NA, NA, NA,
  443160, 1136350, 2182333, 2897821, 3402672, 3873311, NA, NA, NA, NA,
  396132, 1333217, 2180715, 2985752, 3691712, NA, NA, NA, NA, NA,
  440832, 1288463, 2419861, 3483130, NA, NA, NA, NA, NA, NA,
  359480, 1421128, 2864498, NA, NA, NA, NA, NA, NA, NA,
  376686, 1363294, NA, NA, NA, NA, NA, NA, NA, NA,
  344014, NA, NA, NA, NA, NA, NA, NA, NA, NA
), nrow=10, ncol = 10, byrow=TRUE)



B <- matrix(c(
  58046, 127970, 476599, 1027692, 1360489, 1647310, 1819179, 1906852, 1950105,
  24492, 141767, 984288, 2142656, 2961978, 3683940, 4048898, 4115760, NA,
  32848, 274682, 1522637, 3203427, 4445927, 5158781, 5342585, NA, NA,
  21439, 529828, 2900301, 4999019, 6460112, 6853904, NA, NA, NA,
  40397, 763394, 2920745, 4989572, 5648563, NA, NA, NA, NA,
  90748, 951994, 4210640, 5866482, NA, NA, NA, NA, NA,
  62096, 868480, 1954797, NA, NA, NA, NA, NA, NA,
  24983, 284441, NA, NA, NA, NA, NA, NA, NA,
  13121, NA, NA, NA, NA, NA, NA, NA, NA
), nrow=9, ncol = 9, byrow=TRUE)
```

#Fix the first column and update all other columns.
#Loop over all rows and perform the subtraction for each row separately.
#fit GLM model according to Piotr's code

```{r}

D_matrix_observed_A <- A
# Perform the operation
for (i in 1:nrow(D_matrix_observed_A)) {
  for (j in ncol(D_matrix_observed_A):2) {
    D_matrix_observed_A[i, j] <- D_matrix_observed_A[i, j] - D_matrix_observed_A[i, j-1]
  }
}
#D_matrix_observed_A #the same as Flip's

df <- D_matrix_observed_A |>
as_tibble() |>
rownames_to_column(var = "accident_year") |>
pivot_longer(
values_to = "count",
cols = starts_with("V"),
names_to = c("development_year")
) |>
mutate(
accident_year = factor(accident_year),
development_year = factor(development_year)
)

model_d <- glm(
formula = count ~ .,
data = df,
family = poisson(link = "log")
)

summary(model_d)#r(1,1) = r(2,1) = 1

prediction_d <- matrix(predict(model_d, newdata = df, "response"), nrow = 10, byrow = TRUE)

D_matrix_predicted <- D_matrix_observed_A
D_matrix_predicted[is.na(D_matrix_predicted)] <- prediction_d[is.na(D_matrix_predicted)]
D_matrix_predicted #the same relsut
```

#with the estimated beta, we can not recover the increments as in (2)
#because assumption is beta_j is the same for every development_year, 

```{r}
coef <- c(1,1,exp(model_d$coefficients)) 

# Name base cell relativities: 
names(coef)[1:2] <- c("accident_year1","development_yearV1")

#coef for development_year: r_(2,j)
#grep("^development_yearV", names(coef)) finds all indices where names start with "development_yearV".
beta <- coef[grep("^development_yearV", names(coef))]

# Sort by the numeric part of the names
sorted_beta <- beta[order(as.numeric(sub("development_yearV", "", names(beta))))]
beta_sum <- sum(sorted_beta)

#normalize beta
beta_estimated <- sorted_beta/beta_sum


#ro, r_(1,j) for coef of accident_year
gamma_1 <- coef[grep("^accident_year", names(coef))]

# Extract the numeric part of the names
numeric_part <- as.numeric(gsub("accident_year", "", names(gamma_1)))

# Sort the data based on the numeric part of the names
# in right order which can be verified by the alpha_estimated. the results match the C_(i,I) exactly. 
sorted_gamma_1 <- gamma_1[order(numeric_part)]


intercept_value <- coef["(Intercept)"]

#C_(i,I), the results are exactly the same as question 1 and 2. 
alpha_estimated <- intercept_value*sorted_gamma_1*beta_sum

alpha_estimated
beta_estimated
alpha_estimated[1]*beta_estimated #increment not the same as the original data  
```

#control whether beta is right 
#calculate development factors (the same result)

```{r}
# Define the function
development_factor <- function(vec) {
  # Initialize an empty vector to store the results
  results <- numeric(9)
  
  # Loop through the vector and calculate f1 to f9
  for (i in 1:9) {
    if (i == 1) {
      # f1 = (index1 + index2) / index1
      results[i] <- (vec[1] + vec[2]) / vec[1]
    } else {
      # f2 to f9 = (index1 + index2 + ... + index_{i+1}) / (index1 + index2 + ... + index_i)
      numerator <- sum(vec[1:(i + 1)])
      denominator <- sum(vec[1:i])
      results[i] <- numerator / denominator
    }
  }
  
  # Return the results
  return(results)
}

# Example usage
development_factor_A <- development_factor(beta_estimated)
print(development_factor_A)
```

#question 4
```{r}
#The nobs() function is a generic function in R that extracts the number of observations used in a model. It works directly with GLM objects.
n <- nobs(model_d)
r <- 18 + 1 #1 intercept

print(n)
print(r)
##36 the residual degrees of freedom
model_d$df.residual
# Compute Pearson's Chi-Square statistic
pearson_residuals <- residuals(model_d, type = "pearson")
pearson_chisq <- sum(pearson_residuals^2)

# Compute the dispersion parameter and print it 
dispersion_parameter <- pearson_chisq / model_d$df.residual
print(dispersion_parameter)
```
