---
title: "reinsurance"
author: "Li Wu"
date: "2025-02-22"
output: pdf_document
---
```{r}

library(gridExtra)

```

#simulate data from type 1 in one-year's period

```{r}
set.seed(123)

  #X: type1  (mean, sd)
    #lnorm: (9.9096,0.42)  norm:   (250791.51, 50557.53)

# Parameters for lognormal distribution (96.08%)
meanlog_lognorm <- 9.9096   # Mean of the lognormal distribution in log scale
sdlog_lognorm <- 0.42   # Standard deviation in log scale

# Parameters for normal distribution (3.92%)
mean_norm <- 250791.51      # Mean of normal distribution
sd_norm <- 50557.53         # Standard deviation of normal distribution

# Create a sequence of all days in a year
dates <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-12-31"), by = "day")

# Set Poisson and Negative Binomial parameters
lambda_poisson <- 3.0563   # Poisson mean claims (May-Agu)
mu_nb <- 8.7480             # Negative Binomial mean claims (Sep-Apr)
size_nb <- 3.5415          # Dispersion parameter

# Function to simulate claim counts based on month
simulate_claims <- function(date) {
  month_num <- as.numeric(format(date, "%m"))  # Extract month number
  if (month_num %in% 5:8) {  # May to October (Poisson)
    rpois(1, lambda_poisson)
  } else {  # Sep to April (Negative Binomial)
    rnbinom(1, size = size_nb, mu = mu_nb)
  }
}

# Simulate claim numbers for each day
claims_per_day <- sapply(dates, simulate_claims)

# Initialize claim amount vector
claim_amounts <- c()

# Function to simulate claim amounts
simulate_claim_amounts <- function(num_claims) {
  if (num_claims == 0) return(numeric(0))  # No claims -> no amounts
  
  # Determine claim type (96.08% lognormal, 3.92% normal)
  is_lognormal <- runif(num_claims) < 0.9608
  
  # Generate claim amounts
  lognormal_claims <- rlnorm(sum(is_lognormal), meanlog = meanlog_lognorm, sdlog = sdlog_lognorm)
  normal_claims <- rnorm(sum(!is_lognormal), mean = mean_norm, sd = sd_norm)
  
  return(c(lognormal_claims, normal_claims))  # Combine both claim types
}

# Generate claim amounts for each day
all_claim_amounts <- lapply(claims_per_day, simulate_claim_amounts)

# Expand into a data frame
claim_data1 <- data.frame(
  Date = rep(dates, times = claims_per_day),
  Claim_Amount = unlist(all_claim_amounts)
)

```


# simulate data from type 2 in one-year's period
```{r}
# Parameters for lognormal distribution (96.08%)
meanlog_lognorm <- 10.381  # Mean of the lognormal distribution in log scale
sdlog_lognorm <- 0.3932   # Standard deviation in log scale

# Parameters for normal distribution (3.92%)
mean_norm <- 2499750.6      # Mean of normal distribution
sd_norm <- 243867.1       # Standard deviation of normal distribution

# Create a sequence of all days in a year
dates <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-12-31"), by = "day")

# Set Poisson and Negative Binomial parameters
lambda_poisson <- 2.1673  # Poisson mean claims (May-Agu)
mu_nb <- 5.7349             # Negative Binomial mean claims (Sep-Apr)
size_nb <- 4.8928          # Dispersion parameter

# Function to simulate claim counts based on month
simulate_claims <- function(date) {
  month_num <- as.numeric(format(date, "%m"))  # Extract month number
  if (month_num %in% 5:8) {  # May to October (Poisson)
    rpois(1, lambda_poisson)
  } else {  # Sep to April (Negative Binomial)
    rnbinom(1, size = size_nb, mu = mu_nb)
  }
}

# Simulate claim numbers for each day
claims_per_day <- sapply(dates, simulate_claims)

# Initialize claim amount vector
claim_amounts <- c()

# Function to simulate claim amounts
simulate_claim_amounts <- function(num_claims) {
  if (num_claims == 0) return(numeric(0))  # No claims -> no amounts
  
  # Determine claim type (96.08% lognormal, 3.92% normal)
  is_lognormal <- runif(num_claims) < 0.9608
  
  # Generate claim amounts
  lognormal_claims <- rlnorm(sum(is_lognormal), meanlog = meanlog_lognorm, sdlog = sdlog_lognorm)
  normal_claims <- rnorm(sum(!is_lognormal), mean = mean_norm, sd = sd_norm)
  
  return(c(lognormal_claims, normal_claims))  # Combine both claim types
}

# Generate claim amounts for each day
all_claim_amounts <- lapply(claims_per_day, simulate_claim_amounts)

# Expand into a data frame
claim_data2 <- data.frame(
  Date = rep(dates, times = claims_per_day),
  Claim_Amount = unlist(all_claim_amounts)
)

```



#Question (5)

```{r}
#Find the XL Cut-Off Point (90th Percentile)
cutoff_type1 <- as.numeric(quantile(claim_data1$Claim_Amount, 0.90))  # Convert to a simple number
cutoff_type2 <- as.numeric(quantile(claim_data2$Claim_Amount, 0.90))



# Create a data frame with both branches' data
df_type1 <- data.frame(Claim_Amount = claim_data1$Claim_Amount)

df_type2 <- data.frame(Claim_Amount = claim_data2$Claim_Amount)

# Plot Branch 1 and Branch 2 histograms side by side
p1 <- ggplot(df_type1, aes(x = Claim_Amount)) +
  geom_histogram(bins = 50, fill = "lightblue", color = "black") +
  geom_vline(xintercept = cutoff_type1, color = "blue", size = 1.5, linetype = "dashed") +
  labs(x = "Claim Size", y = "Frequency", title = "Branch 1: 90th Percentile") +
  theme_minimal()

p2 <- ggplot(df_type2, aes(x = Claim_Amount)) +
  geom_histogram(bins = 50, fill = "lightblue", color = "black") +
  geom_vline(xintercept = cutoff_type2, color = "blue", size = 1.5, linetype = "dashed") +
  labs(x = "Claim Size", y = "Frequency", title = "Branch 2: 90th Percentile") +
  scale_x_log10() +
  theme_minimal() 

# Arrange the two plots side by side
grid.arrange(p1, p2, ncol = 2)

```


```{r}
#The reinsurer covers claim amounts above the cut-off, so we split each claim into:
#Insurer's share (below cut-off)
#Reinsurer's share (above cut-off)


# Apply XL-Cover
insurer_D_type1 <- pmin(claim_data1$Claim_Amount, cutoff_type1)
reinsurer_R_type1 <- pmax(claim_data1$Claim_Amount - cutoff_type1, 0)

insurer_D_type2 <- pmin(claim_data2$Claim_Amount, cutoff_type2)
reinsurer_R_type2 <- pmax(claim_data2$Claim_Amount - cutoff_type2, 0)


#Price the Reinsurance Contract
reinsurer_cost_type1 <- mean(reinsurer_R_type1) * 1.2
reinsurer_cost_type2 <- mean(reinsurer_R_type2) * 1.2

#the claim amount after reinsurance

reinsurer_claimsAmount_type1 <- insurer_D_type1 + reinsurer_cost_type1
reinsurer_claimsAmount_type2 <- insurer_D_type2 + reinsurer_cost_type2

XL_type1 <- data.frame(
  Claims = c(claim_data1$Claim_Amount, reinsurer_claimsAmount_type1),
  Reinsurance = rep(c("Before XL-Reinsurance", "After XL-Reinsurance"), each = length(claim_data1$Claim_Amount))
)

XL_type2 <- data.frame(
  Claims = c(claim_data2$Claim_Amount, reinsurer_claimsAmount_type2),
  Reinsurance = rep(c("Before XL-Reinsurance", "After XL-Reinsurance"), each = length(claim_data2$Claim_Amount))
)

#Visualize the Impact of XL-Reinsurance
# Plot histogram with density curves
p3 <- ggplot(XL_type1, aes(x = Claims, color = Reinsurance)) +
  geom_histogram(aes(y = ..density..), position = "identity", bins = 50, fill = "gray", color = "black", alpha = 0.5) +  
  geom_density(lwd = 1) +  # Add fitted density curve
  scale_x_log10() +  # Use log scale to handle skewed data
  geom_vline(xintercept = cutoff_type2, color = "blue", linetype = "dashed", size = 1)+
  labs(title = "Branch 1: XL Cover at 90th Percentile ", 
       x = "Total Claim Amount", y = "Density") +
  theme_minimal() +
  theme(legend.position = "none")
#+facet_wrap(~ Reinsurance) #show two histgram side by side 
#The histogram in the plot represents the entire dataset, not separated into 'before' and 'after' categories. so it doesn't match perfectly either of them seperately

p4 <- ggplot(XL_type2, aes(x = Claims, color = Reinsurance)) +
  geom_histogram(aes(y = after_stat(density)), position = "identity", bins = 50, fill = "gray", color = "black", alpha = 0.5) +  
  geom_density(lwd = 1) +  # Add fitted density curve
  scale_x_log10() +  # Use log scale to handle skewed data
  geom_vline(xintercept = cutoff_type2, color = "blue", linetype = "dashed", size = 1)+
  labs(title = "Branch 2: XL Cover at 90th Percentile",
       x = "Total Claim Amount", y = "Density") +
  theme_minimal()+
  theme(legend.title = element_text(size = 5),
        legend.text = element_text(size = 7), 
        legend.position = "bottom")  
grid.arrange(p3, p4, ncol = 2)
```

#(6)
#fuction to simulte total claims

```{r}
 #X: type1  (mean, sd)
    #lnorm: (9.9096,0.42)  norm:   (250791.51, 50557.53)
simulate_function_type1 <- function(){
# Parameters for lognormal distribution (96.08%)
meanlog_lognorm <- 9.9096   # Mean of the lognormal distribution in log scale
sdlog_lognorm <- 0.42   # Standard deviation in log scale

# Parameters for normal distribution (3.92%)
mean_norm <- 250791.51      # Mean of normal distribution
sd_norm <- 50557.53         # Standard deviation of normal distribution

# Create a sequence of all days in a year
dates <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-12-31"), by = "day")

# Set Poisson and Negative Binomial parameters
lambda_poisson <- 3.0563   # Poisson mean claims (May-Agu)
mu_nb <- 8.7480             # Negative Binomial mean claims (Sep-Apr)
size_nb <- 3.5415          # Dispersion parameter

# Function to simulate claim counts based on month
simulate_claims <- function(date) {
  month_num <- as.numeric(format(date, "%m"))  # Extract month number
  if (month_num %in% 5:8) {  # May to October (Poisson)
    rpois(1, lambda_poisson)
  } else {  # Sep to April (Negative Binomial)
    rnbinom(1, size = size_nb, mu = mu_nb)
  }
}

# Simulate claim numbers for each day
claims_per_day <- sapply(dates, simulate_claims)

# Initialize claim amount vector
claim_amounts <- c()

# Function to simulate claim amounts
simulate_claim_amounts <- function(num_claims) {
  if (num_claims == 0) return(numeric(0))  # No claims -> no amounts
  
  # Determine claim type (96.08% lognormal, 3.92% normal)
  is_lognormal <- runif(num_claims) < 0.9608
  
  # Generate claim amounts
  lognormal_claims <- rlnorm(sum(is_lognormal), meanlog = meanlog_lognorm, sdlog = sdlog_lognorm)
  normal_claims <- rnorm(sum(!is_lognormal), mean = mean_norm, sd = sd_norm)
  
  return(c(lognormal_claims, normal_claims))  # Combine both claim types
}

# Generate claim amounts for each day
all_claim_amounts <- lapply(claims_per_day, simulate_claim_amounts)

# Expand into a data frame
claim_data1 <- data.frame(
  Date = rep(dates, times = claims_per_day),
  Claim_Amount = unlist(all_claim_amounts)
)
}

simulate_function_type2 <- function(){
# Parameters for lognormal distribution (96.08%)
meanlog_lognorm <- 10.381  # Mean of the lognormal distribution in log scale
sdlog_lognorm <- 0.3932   # Standard deviation in log scale

# Parameters for normal distribution (3.92%)
mean_norm <- 2499750.6      # Mean of normal distribution
sd_norm <- 243867.1       # Standard deviation of normal distribution

# Create a sequence of all days in a year
dates <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-12-31"), by = "day")

# Set Poisson and Negative Binomial parameters
lambda_poisson <- 2.1673  # Poisson mean claims (May-Agu)
mu_nb <- 5.7349             # Negative Binomial mean claims (Sep-Apr)
size_nb <- 4.8928          # Dispersion parameter

# Function to simulate claim counts based on month
simulate_claims <- function(date) {
  month_num <- as.numeric(format(date, "%m"))  # Extract month number
  if (month_num %in% 5:8) {  # May to October (Poisson)
    rpois(1, lambda_poisson)
  } else {  # Sep to April (Negative Binomial)
    rnbinom(1, size = size_nb, mu = mu_nb)
  }
}

# Simulate claim numbers for each day
claims_per_day <- sapply(dates, simulate_claims)

# Initialize claim amount vector
claim_amounts <- c()

# Function to simulate claim amounts
simulate_claim_amounts <- function(num_claims) {
  if (num_claims == 0) return(numeric(0))  # No claims -> no amounts
  
  # Determine claim type (96.08% lognormal, 3.92% normal)
  is_lognormal <- runif(num_claims) < 0.9608
  
  # Generate claim amounts
  lognormal_claims <- rlnorm(sum(is_lognormal), meanlog = meanlog_lognorm, sdlog = sdlog_lognorm)
  normal_claims <- rnorm(sum(!is_lognormal), mean = mean_norm, sd = sd_norm)
  
  return(c(lognormal_claims, normal_claims))  # Combine both claim types
}

# Generate claim amounts for each day
all_claim_amounts <- lapply(claims_per_day, simulate_claim_amounts)

# Expand into a data frame
claim_data2 <- data.frame(
  Date = rep(dates, times = claims_per_day),
  Claim_Amount = unlist(all_claim_amounts)
)}



#simulate 3000 times of the yearly total claim amount 
total_claim1 <- replicate(3000, sum(simulate_function_type1()$Claim_Amount))
total_claim2 <- replicate(3000, sum(simulate_function_type2()$Claim_Amount))
```




```{r}
#Simulate the claims amount in one year for both Type 1 and Type 2. Then add them to get the total

# Determine SL Cut-Off Points
sl_cutoff1 <- quantile(total_claim1, 0.90)
sl_cutoff2 <- quantile(total_claim2, 0.90)

#Apply SL-Cover Reinsurance
insurer_claims1 <- pmin(total_claim1, sl_cutoff1)
reinsurer_claims1 <- pmax(total_claim1 - sl_cutoff1, 0)

insurer_claims2 <- pmin(total_claim2, sl_cutoff2)
reinsurer_claims2 <- pmax(total_claim2 - sl_cutoff2, 0)

# Expected reinsurer cost and pricing (130% of expected cost)
expected_reinsurer_cost1 <- mean(reinsurer_claims1)
expected_reinsurer_cost2 <- mean(reinsurer_claims2)

# Price of SL reinsurance contract
reinsurance_price1 <- expected_reinsurer_cost1 * 1.3
reinsurance_price2 <- expected_reinsurer_cost2 * 1.3

# amount after SL reinsurance
reinsurer_claims1 <- insurer_claims1 + reinsurance_price1
reinsurer_claims2 <- insurer_claims2 + reinsurance_price2
  
  
# Create data frame for visualization
df_SL1 <- data.frame(
  Claims = c(total_claim1, reinsurer_claims1),
  Type = rep(c("Before SL-Reinsurance", "After SL-Reinsurance"), each = length(total_claim1))
)

df_SL2 <- data.frame(
  Claims = c(total_claim2, reinsurer_claims2),
  Type = rep(c("Before SL-Reinsurance", "After SL-Reinsurance"), each = length(total_claim2))
)

# Plot histogram with density lines
p5 <- ggplot(df_SL1, aes(x = Claims, color = Type)) +
  geom_histogram(aes(y = ..density..), position = "identity", bins = 50, fill = "gray", color = "black", alpha = 0.5) +  
  geom_density(lwd = 1.2) +  # Add smooth density curve
  scale_x_log10() + # Log scale to improve visualization
  geom_vline(xintercept = sl_cutoff1, color = "blue", linetype = "dashed", size = 1)+
  labs(title = "Branch 1: Impact of SL on S(t) Distribution", 
       x = "Total Claim Amount", y = "Density") +
  theme_minimal()+
  theme(legend.position = "none")

p6 <- ggplot(df_SL2, aes(x = Claims, color = Type)) +
  geom_histogram(aes(y = ..density..), position = "identity", bins = 50, fill = "gray", color = "black", alpha = 0.5) +  
  geom_density(lwd = 1.2) +  # Add smooth density curve
  scale_x_log10() +  # Log scale to improve visualization
  geom_vline(xintercept = sl_cutoff2, color = "blue", linetype = "dashed", size = 1)+
  labs(title = "Branch 2", 
       x = "Total Claim Amount", y = "Density") +
  theme_minimal()+
  theme(legend.title = element_text(size = 5),
        legend.text = element_text(size = 7), 
        legend.position = "bottom")  
grid.arrange(p5, p6, ncol = 2)
#Why do we have such a high number of claims at the cut-off point? It's because all claims that exceed this threshold are counted in this interval.
```

#(7) a single SL-cover for the total claim cost for the entire company.

```{r}

total_claim <- total_claim1 + total_claim2

# Determine SL Cut-Off Points
sl_cutoff <- quantile(total_claim, 0.90)

#Apply SL-Cover Reinsurance
insurer_claims <- pmin(total_claim, sl_cutoff)
reinsurer_claims <- pmax(total_claim - sl_cutoff, 0)


# Expected reinsurer cost and pricing (130% of expected cost)
expected_reinsurer_cost <- mean(reinsurer_claims)

# Price of SL reinsurance contract
reinsurance_price <- expected_reinsurer_cost * 1.3

# amount after SL reinsurance
reinsurer_claims <- insurer_claims + reinsurance_price
  
  
# Create data frame for visualization
df_SL <- data.frame(
  Claims = c(total_claim, reinsurer_claims),
  Type = rep(c("Before SL-Reinsurance", "After SL-Reinsurance"), each = length(total_claim1))
)


# Plot histogram with density lines
ggplot(df_SL, aes(x = Claims, color = Type)) +
  geom_histogram(aes(y = ..density..), position = "identity", bins = 50, fill = "gray", color = "black", alpha = 0.5) +  
  geom_density(lwd = 1.2) +  # Add smooth density curve
  scale_x_log10() + # Log scale to improve visualization
  geom_vline(xintercept = sl_cutoff, color = "blue", linetype = "dashed", size = 1)+
  labs(title = "Branch 1 and 2: Impact of SL on S(t) Distribution", 
       x = "Total Claim Amount", y = "Density") +
  theme_minimal()

```
#(8)Based on the results from the previous sections, we would recommend either an SL cover or a joint SL cover. In both cases, we have nearly the same risk exposure at the 90th percentile, but we eliminate the potential risk in the region above the 90th percentile.
```{r}


```



```{r}

```

